Internet of Things: a Real-World Deployment Towards Smart Grids Integration

### 2013-07-08 doc/thesis/report.tex

\chapter{Abstract}
\paragraph{}
Information Technology is growing exponentially and largely impacting our daily lives. The current evolution in computing is the \gls{iot}. It is smoothly evolving from an Internet of people to and Internet of \textit{Things}. By 2020, it is expected to have 50 billion \textit{Things} connected to the Internet. 
\paragraph{}
However, such a migration induces a strong level of complexity when handling interoperability between heterogeneous \textit{Things}, e.g. Wireless Sensors, RFID, and mobile devices.
\paragraph{}
In this thesis, we focus on the integration of wireless sensors into \gls{iot}. This is a prologue for the future integration of \gls{sg} into \gls{iot}. In this work, we deployed a smart building test-bed for energy optimization, and for integration into \gls{sg}\glsreset{sg}.
\paragraph{}
The test-bed built provides IPv6 gatewaying, remote control of wireless sensor nodes which is built on top of \gls{6lowpan}\glsreset{6lowpan}, and mobile access to the system.
\paragraph{}
The system is using different technologies such as \gls{tinyos}, \gls{nesc}, \gls{j2se} and  \gls{http}.

>>>>

\chapter{Abstract}
\paragraph{}
Information Technology is growing exponentially and largely impacting our daily lives. The current evolution in computing is the \gls{iot}. The Internet is smoothly evolving from an Internet of people to and Internet of \textit{Things}. By 2020, it is expected to have 50 billion \textit{Things} connected to the Internet. 
\paragraph{}
However, such a migration induces a strong level of complexity when handling interoperability between heterogeneous \textit{Things}, e.g. Wireless Sensors, RFID, and mobile devices.
\paragraph{}
This thesis focuses on the development of an \gls{iot} test-bed, using wireless sensors, that will be used for smart grid applications.
\paragraph{}
The test-bed built provides IPv6 gatewaying, remote control of wireless sensor nodes which is built on top of \gls{6lowpan}\glsreset{6lowpan}, and mobile access to the system.
\paragraph{}
The system is using different technologies such as \gls{tinyos}, \gls{nesc}, \gls{j2se} and  \gls{http}.
